### 2017-04-04 thesis/latex/thesis.tex
Thesis: small touchup.

\subsection{Interest builder}
Begin with a paper-like introduction which talks about:

\begin{itemize}
\item How dynein is a structure which turns chemical energy into motion
\item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
\item How it's weird that a cellular structure can generate directed motion
\item Other cool stuff - make dynein mysterious and cool.
\end{itemize}

Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it

@@

This thesis aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern. To do this, an artificial motor model is created which exhibits flexibility and is affected by Brownian motion. This model is then simulated, and its behavior are compared to the behavior of real dynein.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist's rendition of dynein.}{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition}
\end{figure}

@@

Diffusion, or random motion of molecules due to collisions with solvent (i.e. Brownian motion), is one possible process cells could use to transport biomolecules. Diffusion has two problems: it is slow and nondirected. The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \textbf{cite here}:

\begin{equation}
  \label{diffusion-equation}
  <x> = \sqrt{2Dt}
\end{equation}
%% \myequations{some equation}

>>>>

%% \subsection{Interest builder}
%% Begin with a paper-like introduction which talks about:

%% \begin{itemize}
%% \item How dynein is a structure which turns chemical energy into motion
%% \item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
%% \item How it's weird that a cellular structure can generate directed motion
%% \item Other cool stuff - make dynein mysterious and cool.
%% \end{itemize}

%% Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it

@@

This thesis describes an experiment which aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern. To do this, a mathematical model of a dynein-like motor is constructed which exhibits flexibility and feels Brownian forces. This model is then simulated, and its behavior is compared to the behavior of real dynein.\\

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist's rendition of dynein bound to a microtubule.}{One monomer is bound to the MT, and the other is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition}
\end{figure}

@@

Diffusion, or random motion of molecules due to collisions with solvent (i.e. Brownian motion), is one possible process cells could use to transport biomolecules. Diffusion has two problems: it is slow and nondirected. The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \cite{einstein-paper}:

\begin{equation}
  \label{diffusion-equation}
  <x> = \sqrt{2Dt}
\end{equation}
